\documentclass{article}

%------------- Packages -------------%
\usepackage[pdftex]{graphicx}
\usepackage[margin=1.25in]{geometry}
\usepackage{float}
\usepackage{microtype}
\usepackage[hidelinks]{hyperref}
\usepackage{multicol}

%------------- Definitions -------------%
\parindent=0pt
\parskip=8pt
\setcounter{secnumdepth}{0}
\sloppy

\begin{document}

%------------- Title Page -------------%
\begin{titlepage}
\begin{center}

~ \\[2cm]
\textsc{\LARGE The Constitution of the}\\[0.5cm]
\textsc{\LARGE Computer Science and Engineering Club}\\[1.0cm]
\textsc{\large California State University, San Bernardino}\\[5cm]
\textsc{\Large 2013 -- 2014 Arrangement}\\[9.2cm]

\begin{minipage}{0.4\textwidth}
\begin{flushleft} \large
~\\
~\\
Revision 1.0 \\
\today
\end{flushleft}
\end{minipage}
~
\begin{minipage}{0.55\textwidth}
\begin{flushright} \large
\emph{Advisors:} \\
Dr. Arturo \textsc{Concepcion}\\
Dr. David \textsc{Turner}\\
Ms. Chingyi \textsc{Wang}
\end{flushright}
\end{minipage}
\end{center}
\end{titlepage}

%------------- Table of Contents -------------%
\newpage
\tableofcontents

%------------- Constitution -------------%
\newpage

\section{Article I. Preamble}
  We, the undersigned, wishing to secure for ourselves the pleasures and benefits of an association of those interested in Computer Science and Engineering, enact this constitution as our governing law.

  \subsection{Section 1. Name}
    The official name of the organization shall be the Computer Science and Engineering Club and may be referred to as the Club throughout the rest of this document. The abbreviation of the Club name shall be CSE Club.

  \subsection{Section 2. Purpose}
    The purpose of the Computer Science and Engineering Club is to
    \begin{itemize}
      \item Form a scholarly, nonpolitical, and nonprofit student association for persons interested in Computer Science and Engineering studies
      \item Promote interest and scientific understanding in Computer Science and Engineering
      \item Promote cooperative activities and exchange of information within the fields of Computer Science and Engineering
      \item Provide a means for the publication of scholarly research and other materials designed to promote Computer Science and Engineering studies
      \item Facilitate contact and exchange of information between scholars and scholarly organizations at CSUSB interested in Computer Science and Engineering and those in other countries
      \item Facilitate the increase in fluency of all computer language learners through partnering and sharing with other Computer Science and Engineering students
      \item Introduce new languages, theories, topics of discussion, and activities to our Computer Science and Engineering students
    \end{itemize}

\section{Article II. Supremacy}
  This Constitution shall be the supreme ruling document for the Computer Science and Engineering Club. The officers of Club shall be the governing body of the Club, and shall establish By-Laws which shall provide rules of conduct for the Club in accordinance with, and subordinate to, this Constitution.

\section{Article III. Membership}

  \subsection{Section 1. Categories of Membership}
    \begin{enumerate}
      \item Membership shall be open to all individuals and groups interested in the field of Computer Science and Engineering Studies.
      \item There shall be four categories of membership:
      \begin{description}
        \item[Student members] ~\\
          Any individual enrolled at CSUSB.
        \item[Regular members] ~\\
          Any individual not enrolled at CSUSB.
        \item[Institutional members] ~\\
          Any group or organization wishing to affiliate for the purpose of receiving Computer Science and Engineering Club publications and announcements.
        \item[Associate members] ~\\
          Any individual not desiring the privileges and responsibilities of regular membership but desiring to participate in a particular function of the Association.
      \end{description}
    \end{enumerate}

  \subsection{Section 2. Requirements}
    \begin{itemize}
      \item Membership dues shall be payable quarterly or yearly.
      \item Any member in arrears for more than two months shall not receive any Club publication or announcements.
      \item Any member in arrears for one full quarter shall, after receiving official notice from the Club, lose his/her/its membership in the Association.
      \item The ultimate authority of the Club shall be vested in the full membership of all members in good standing.
      \item This authority shall be expressed in voting at either the annual membership meeting or through mail polls conducted by the officers and council of the Club. Only student members shall be entitled to vote and hold office.
      \item Institutional members shall only receive publications and announcements of the Club.
    \end{itemize}

  \subsection{Section 3. Suspension}
    A member may be removed from membership due to disorderly conduct, gross misdemeanor, failure to fulfill requirements of their membership, category, or any other reason important to the organization. A member may be suspended or removed for the above stated reasons following a hearing by the membership of the organization, with final authority given by the board of officers.

\section{Article IV. Officers}

  \subsection{Section 1. Positions}
    The Association’s officers shall be the President, the Vice-President, the Treasurer and the Secretary and other positions as deemed by the Club officers and filled by the membership.

  \subsection{Section 2. Roles}
    \begin{description}
      \item[President] ~\\
        The President serves as the executive officer of the Club, and is responsible for the overall running of the Club. The President acts as the Club's primary spokesperson and representative.

        The President has the power of appointment. He or she may appoint individuals to serve in various positions to assist the elected officers of the Club. These appointments require confirmation by the Board of officers by a majority vote.

      \item[Vice President] ~\\
        The Vice President shall be to serve as President when the President is unavailable. He or she shall also perform other duties as directed by the President to encourage participation and growth of the Club.

      \item[Treasurer] ~\\
        The Treasurer shall be responsible for all accounts and bookkeeping of funds for the treasury of the Club.

      \item[Secretary] ~\\
        The Secretary shall ensure the order of Club meetings and documents, and acts as a communication channel for the Club.
    \end{description}

  \subsection{Section 3. Requirements}
    \begin{itemize}
      \item An officer must fullfill their duties, as stated in the By-laws of the Club.
      \item The officers of the Club are also members of the Club, and thus are held to the same requirements as members of the Club.
    \end{itemize}

  \subsection{Section 4. Compensation}
    No appointed or elected officers of the Club shall receive any financial compensation for services rendered to or on behalf of the Club, except for reimbursement of personal expenses incurred by officers of the Club in the course of their work on behalf of the Club. Exceptions may be granted by a recommendation by the President and a 2/3 vote of the Board of officers excluding the affected member(s).

  \subsection{Section 5. Impeachment}
    Impeachment of any officer will be attained only after review and trial by the board of an accusation worthy of dismissal as a member or conduct not befitting the office, with a 2/3 vote of the board of elected and appointed officers, excluding that officer.

\section{Article VII. Amendments}
  Amendments to the constitution may be made by recommendation from the board of officers and a three quarter affirmative vote by a quorum at the second meeting of the year after elections are held, and only after presentation and discussion at one other meeting.

\section{Article VIII. Non-discrimination}
  The Computer Science and Engineering Club shall never discriminate by race, religion, natural origin, ethnicity, color, age, gender, marital status, citizenship, sexual orientation, and/or disability.

\section{Article IX. Non-hazing}
  Neither the Computer Science and Engineering Club, nor its members, shall conspire to engage in hazing, participate in hazing, commit any act that injures, degrades, or disgraces or tends to injure, degrade, or disgrace any fellow student or person attending the institution.

\section{Article X. Off-Campus Issues}
  The Computer Science and Engineering Club, or its members, when taking stands on issues, recognizes and will fulfill its obligation to make clear that it in no way represents the official position of the California State University, San Bernardino.

%------------- By-laws -------------%
\newpage
\section{By-laws}
  A majority vote of the board of officers is required to change the bylaws after the change has been discussed at one meeting and may be done so only after elections.

  \subsection{Article I. Appointments}

    \subsubsection{Section 1. Webmaster}
      The board wishes to include in its officers the position of Webmaster. His or her role will be to create and maintain a website for the Club.

    \subsubsection{Section 2. Information Officer}
      The board wishes to include in its officers the position of Information Officer. His or her role will be to keep the members informed about meetings and upcoming events and to, at the request of members of The Board, invite dignitaries, company representatives and representatives of CSUSB organizations.

  \subsection{Article II. Duties}
    The duties of each officer position include, but are not limited to:

    \begin{description}
        \item[President] ~\\
          \vspace{-12pt}
          \begin{itemize}
            \item Always act in the best interests of the Club.
            \item Ensure that the Club continues to grow and reach out to new individuals.
            \item Enforce the observence of the Constitution and Bylaws.
            \item Sign all official documents adopted by the Club.
            \item Conduct meetings according to the rules adopted.
          \end{itemize}
        \item[Vice President] ~\\
          \vspace{-12pt}
          \begin{itemize}
            \item Assume the duties of the President when he or she is unavailable.
            \item Encourage the growth of the club.
          \end{itemize}
        \item[Treasurer] ~\\
          \vspace{-12pt}
          \begin{itemize}
            \item Keep an account of all incoming and outgoing funds of the Club treasury.
            \item Disburse funds when requested and approved by the board.
            \item Collect membership dues.
            \item Keep the board members and faculty advisor appraised of funds available and expenses paid at regular and frequent intervals.
          \end{itemize}
        \item[Secretary] ~\\
          \vspace{-12pt}
          \begin{itemize}
            \item Keep the minutes of the board meetings and maintain them for review.
            \item Ensure that meetings are effectively organized and recorded.
            \item Facilitate communication of records between members of the Club.
            \item Maintain and organize all documents of the Club.
          \end{itemize}
        \item[Webmaster] ~\\
          \vspace{-12pt}
          \begin{itemize}
            \item Create and maintain a website for the Club
            \item Turn over control to the Club at the end of his or her term.
            \item Be responsible for the security of the website.
            \item Be responsible for the content of the website.
          \end{itemize}

          Design of the website will be at the discretion of the board. Any costs incurred will be paid out of club funds, upon approval of the board.

        \item[Information Officer] ~\\
          \vspace{-12pt}
          \begin{itemize}
            \item Disseminate information about the Club to its membership, associations, and entities.
            \item Be responsible for Club tutorial and instructional activities.
          \end{itemize}
        \end{description}

  \subsection{Article III. Meetings}

    \subsubsection{Section 1. Rules of Order}
      All meetings shall be conducted in accordinance with Robert's Rules of Order, Newly Revised in all cases in which it is applicable and not inconsistent with these by-laws, the Constitution, or rules of the university.

    \subsubsection{Section 2. Quorum}
      The attendance of half the officers constitutes a quorum for the transaction of business at a board meeting. The attendance of half the officers and one third of the members constitute a quorum for the transaction of business at a special meeting. A special meeting of the entire membership may be called for any purpose as directed by the president and the board of officers for the purpose of including the membership in decisions.

    \subsubsection{Section 3. Schedule}
      Meetings are to be held at least once a month, or by arrangement. Special meetings may be called, however, a quorum must be present at all special meetings, and only the business for which a special meeting has been called may be transacted at the meeting. Members will be notified via email of all meetings.

  \subsection{Article IV. Finances}

    \subsubsection{Section 1. Banking}
      The treasury shall be kept at an off campus bank of the board of officers choosing. There shall be two signatures required on all transactions, president and treasurer.

    \subsubsection{Section 2. Membership Dues}
      Membership dues will be \$15 per quarter, or \$35 per year. Dues will be collected once per quarter.

    \subsubsection{Section 3. Dispersal of Funds}
      In the event that this organization does not becomes and remains inactive during a two-year period, any funds remaining in the account are to be transferred to Computer Science and Engineering department, under the direction of a faculty advisor, as contributions to scholarship funds.


  \subsection{Article V. Elections}

    \subsubsection{Section 1. Nominations}
      Nominations of oneself or another interested party will be allowed by informing the board of the intent to run for office via mail, email or spoken word.

    \subsubsection{Section 2. Time of Elections}
      Elections will be held annually at the end of, but prior to the completion of, the Spring Quarter.

    \subsubsection{Section 3. Procedures}
      Officers are elected by secret ballot, to be facilitated by the Club and with cooperation of the department of Computer Science and Engineering. A plurality vote is required to win and fill a position.

      In the event of a tie, the decision of a split election shall be decided by a pseudo-random number generator where candidates are associated with even representations of numbers.  Such decisions shall be done using an open-source code written by neither of the nominees and reviewed by the Board.  The code shall be run and the decision shall be made at a club meeting where 1/3 of student members and both nominees are present.

    \subsubsection{Section 4. Assumptions of Office}
      Newly elected officers will assume the office at the monthly meeting following elections and will remain in office for one full year.

    \subsubsection{Section 5. Vacancies}
      If the President should resign, be recalled, or die, then the Vice President shall complete the remainder of the term in the President’s position. A new Vice President will be elected by general vote of the student members.  Other Board positions will be filled by general vote by the student members.

  \subsection{Article VI. Advisor}
    Advisors will be selected at the discretion of the Board of officers with a two-thirds majority vote. Advisors will be re-affirmed automatically on a yearly basis unless the desire to step down has been noted or the Board wishes to include other advisors. An Advisor may be removed from position under the same rules for removal of an officer of the Club.

  \subsection{Article VII. Customs}
    \subsection{Section 1. Code of Ethics}
      Members of the Club are expected to be committed to ethical professional conduct, and should use the Association for Computing Machine's Code of Ethics as a general guideline for making ethical decisions.
    \subsection{Section 2. Software Licensing}
      Any and all work that is performed on a group project with other club members, and organized by the club, will be considered as belonging to the CSE Club and may be published as such with appropriate recognition to the contributors.

      It is in the nature of the Club to facilitate open learning, and as such, software written by the Club is encouraged to be released as open source, either with an MIT, BSD, or GPL compatible license.

  \section{Signatures}
    This constitution was approved by a majority vote of the general membership of the Computer Science and Engineering Club on the 17th of May, year 2013.\\[0.4in]

  \begin{multicols}{2}
    Russel Morgan, President\\[0.2in]

    William Elder, Treasurer\\[0.2in]

    Dylan Allbee, Webmaster\\[0.2in]

    Andrew Brinker, Vice-President\\[0.2in]

    Abigail Legg, Secretary\\[0.2in]

    Angelica Escolero, Information Officer\\
  \end{multicols}

\end{document}
